---
title: "Leaflet"
author: "Willem Hogewoning"
date: "4-4-2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Peer-graded Assignment: R Markdown and Leaflet

Create a web page using R Markdown that features a map created with Leaflet. 

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity! 

Create empthy map:
```{r, eval=FALSE}
library(leaflet)
my_map <- leaflet() %>% 
  addTiles()
my_map
```

## at list of ship wrecks
(Sourse = https://wrecks.nauticalcharts.noaa.gov/downloads/AWOIS_Wrecks.xls)

USS MILWAUKEE	40,8123	-124,196833
USS NEW JERSEY	35,03218	-75,290439
USS PC 463	25,947042	-82,874836
USS VIRGINA	35,01929	-75,285944

```{r, eval=FALSE}

Ships <- data.frame(
  lat = c(40.8123, 35.03218, 25.947042, 35.01929),
  lng = c(-124.196833, -75.290439, -82.874836, -75.285944))

Names <- c("USS MILWAUKEE", "USS NEW JERSEY", "USS PC", "USS VIRGINA")
  
my_map <- my_map %>%
  addMarkers(lat=Ships$lat, lng = Ships$lng, 
             popup=Names, 
  clusterOptions = markerClusterOptions() )
my_map
```




```